Betting and Belief: Prediction Markets and Attribution of Climate Change

### 2016-03-27 prediction_market_wsc.Rnw
the reason it wouldn’t compile from tex to pdf was the "\texttt{idea}_i” you added which should be “$\texttt{idea}_i$”, and mainly because you added this line "\SweaveOpts{concordance=TRUE}”.

%#########################################################
%*
%*  The Document.
%*
\begin{document}
\SweaveOpts{concordance=TRUE}

@@

    Formally, in each period, trader $i$ picks her buying or selling price for $s$ uniformly at random in the interval  
    $[(1 - \texttt{risk.tak}_i) \texttt{reserv}_{i}, \allowbreak  \texttt{reserv}_{i,t}]$ for buying and 
    $[\texttt{reserv}_{i}, \allowbreak (1  + \texttt{risk.tak}_i) \texttt{reserv}_{i,t}]$ for selling. 
  \item  \texttt{ideo} :  determines the degree of ``ideology'' of traders.
    For each trader $i$, the level of $\texttt{ideo}_i$ is drawn uniformly at random from $[0,\texttt{ideo}]$.
    If \texttt{ideo} is high, traders will not revise their approximate models easily, even when faced with evidence that their richest neighbor is doing better than them. 
    Formally, for each trader $i$ and each sequence, \texttt{ideo}_i is the probability that $i$ adopts the approximate model of her richest neighbor if that neighbor is doing better than $i$ at the end of the sequence (in monetary terms).
  \end{itemize}
\end{itemize}

>>>>

%#########################################################
%*
%*  The Document.
%*
\begin{document}

@@

    Formally, in each period, trader $i$ picks her buying or selling price for $s$ uniformly at random in the interval  
    $[(1 - \texttt{risk.tak}_i) \texttt{reserv}_{i}, \allowbreak  \texttt{reserv}_{i,t}]$ for buying and 
    $[\texttt{reserv}_{i}, \allowbreak (1  + \texttt{risk.tak}_i) \texttt{reserv}_{i,t}]$ for selling. 
  \item  \texttt{ideo} :  determines the degree of ``ideology'' of traders.
    For each trader $i$, the level of $\texttt{ideo}_i$ is drawn uniformly at random from $[0,\texttt{ideo}]$.
    If \texttt{ideo} is high, traders will not revise their approximate models easily, even when faced with evidence that their richest neighbor is doing better than them. 
    Formally, for each trader $i$ and each sequence, $\texttt{ideo}_i$ is the probability that $i$ adopts the approximate model of her richest neighbor if that neighbor is doing better than $i$ at the end of the sequence (in monetary terms).
  \end{itemize}
\end{itemize}
